Predicting Success of Motivational Interviews with Recurrent Neural Network and Probabilistic Model for Patient-Provider Communication Sequences

### 2017-09-01 paper-amia-summit-2018/amia_summit_2018.tex
prediction method

\subsection*{\textit{Prediction method}}
Generally, a sequence is a temporally ordered set of events. In this study, an event is a behavior code that also has a symbolic representation, such as 117 $LUP+$ (low uptake, positive), 331 $OQ-ECT+$ (open-ended question, elicit change talk positive), etc.  Given a sequence of behavior codes $S_i = \{c_1, c_2,...,c_n\}$ representing patient-provider communication exchanges during some part of a motivational interview, the task of predicting interview success can be viewed as sequence classification. Given a set of class labels $L = \{l_1, l_2,...,l_m\}$ (in our case, the labels are ``successful'' and ``unsuccessful'' motivational interview), a sequence classifier $C$ learns a function $S_i \to l_i, l_i \in L$ that maps a sequence $S_i$ into a class label $l_i \in L$.

>>>>

\subsection*{\textit{Prediction method}}
Generally, a sequence is a temporally ordered set of events. In this study, an event is a behavior code that also has a symbolic representation, such as $LUP+$ (low uptake, positive), $OQECHT+$ (open-ended question, elicit change talk positive), etc.  Given a sequence of behavior codes $S_i = \{c_1, c_2,...,c_n\}$ representing patient-provider communication exchanges during some part of a motivational interview, the task of predicting interview success can be viewed as sequence classification. Given a set of class labels $L = \{l_1, l_2,...,l_m\}$ (in our case, the labels are ``successful'' and ``unsuccessful'' motivational interview), a sequence classifier $C$ learns a function $S_i \to l_i, l_i \in L$ that maps a sequence $S_i$ into a class label $l_i \in L$.
